Natural Selection Across Three Generations of Americans

### 2024-02-23 hrs-selection.qmd
tweaks

tidy_coefs |> 
  # Select only the interaction terms:
  filter(grepl(":", term)) |> 
  mutate(.by = c(pgs, interaction),
    PGS = pgs,
    # gets the pretty name of the group
    Split = names(interactions)[match(interaction, interactions)],
    Group = c("Unprivileged", "Privileged"),
    Difference = ifelse(test.p.value < 0.05, "Difference p < 0.05",
                        "Difference n.s.")
  ) |> 
  ggplot(aes(estimate, Split, colour = Group)) + 
    geom_linerange(aes(xmin = conf.low, xmax = conf.high), alpha = 0.5,
                   position = pos_dod) +
    geom_point(aes(shape = Group, colour = Group, fill = Difference),
               position = pos_dod, 
               shape = "circle filled", size = 2) +
    facet_wrap(vars(PGS), ncol = 1) +
    scale_fill_manual(values = c("n.s." = "white", 
                                 "p < 0.05" = "orange"),
                                 guide = guide_legend(title = NULL)) +
    scale_color_manual(values = c("Privileged" = "steelblue4", 
                                  "Unprivileged" = "red4")) +
    theme_minimal() +
    theme(
      panel.grid.major.y = element_blank(),
      panel.grid.minor.x = element_blank()
    ) + 
    labs(x = "Coefficient on RLRS", y = "")

>>>>

tidy_coefs |> 
  # Select only the interaction terms:
  filter(grepl(":", term)) |> 
  mutate(.by = c(pgs, interaction),
    PGS = pgs,
    # gets the pretty name of the group
    Split = names(interactions)[match(interaction, interactions)],
    Group = c("Disadvantaged", "Advantaged"),
    Difference = ifelse(test.p.value < 0.05, "Difference p < 0.05",
                        "Difference n.s.")
  ) |> 
  ggplot(aes(estimate, Split, colour = Group)) + 
    geom_linerange(aes(xmin = conf.low, xmax = conf.high), alpha = 0.5,
                   position = pos_dod) +
    geom_point(aes(shape = Group, colour = Group, fill = Difference),
               position = pos_dod, 
               shape = "circle filled", size = 2) +
    facet_wrap(vars(PGS), ncol = 1) +
    scale_fill_manual(values = c("Difference n.s." = "white", 
                                 "Difference p < 0.05" = "orange"),
                                 guide = guide_legend(title = NULL)) +
    scale_color_manual(values = c("Advantaged" = "steelblue3", 
                                  "Disadvantaged" = "red4")) +
    theme_minimal() +
    theme(
      panel.grid.major.y = element_blank(),
      panel.grid.minor.x = element_blank()
    ) + 
    labs(x = "Coefficient on RLRS", y = "")
